Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2020-01-10 paper.tex
Fixing minor errors. Added statement about fixing Figure 7. Final versions to be submitted.
Removing bolded text from .tex file for next revision.

In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background \textbf{at the instance of star formation}, augmenting results from prior work. We aim to provide further insight into the host haloes of Pop III stars. In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding are described. In \S 3 we present the results of our analysis. In \S 4 we discuss the results in more detail and compare with previous work. In \S 5 we conclude our discussion with a summary of our results and the implications therein.

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter particle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior. The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. \textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.

@@

If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance. \textbf{We ran another 1~Mpc$^3$ simulation with the same setup as the main simulation with the exception that it was a zoom-in simulation focusing on a single minihalo of mass $5 \times 10^5~\Ms$ collapsing at $z \simeq 23$.  Starting from 1~Myr before the collapse, we followed Pop III star formation in this one halo with a merging distance of 10, 5, 2.5, 1.25, and 0.625~pc.  We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.  We note that our density threshold for star particle formation is equivalent to a molecular core.  Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU within molecular cores \citep[e.g.][]{Turk09, Stacy11}, therefore our results on multiplicity should be considered as lower limits.}

The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from the W12 choice of 100 M$_{\odot}$. This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above. \textbf{The Pop III IMF mass ranges from $1 \leq M / M_{\odot} \leq 300$. }Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. \textbf{Again, we are only tracking the formation of metal-free molecular cores, which form either a single or multiple massive Pop III stars and perhaps several more low mass stars.}

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a \textbf{realistic \hh{} halo profile}, and use Equation \ref{shield} to calculate the shielding factor. The \hh{} molecule number density within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density. Here, H$_{0}$ is the Hubble constant, G is the gravitational constant, and z is the redshift. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift, and for a given \hh{} fraction halo profile. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at $z = 24.1$ from \citet{OShea08} (their Figure 13d) with $J_{21} = 0$, which was extracted directly from their plot. These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(r) - 3.039$ for $r < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(r) - 2.737$ for $r > 3.5$ pc}. 
As the halo masses increase, the shielding factor \textbf{decreases}, meaning there is \textbf{more} shielding occurring within that halo. This behavior occurs \textbf{because as halo masses increase, more \hh{} is being added to the calculation of the column density. The more \hh{} present within a halo, the smaller the shielding factor will become}. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a Doppler broadening parameter $ b = 10 \kms$. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these haloes is almost at a maximum. Self-shielding will then significantly decrease the dissociation rate of \hh{} in the halo core, allowing for the presence of a significant \hh{} fraction even in a strong LW background.

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ haloes that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. When the first Pop III star forms in our simulation at $z = 27$, there are only 6 haloes that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}. These Pop III stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, haloes form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of $J_{21}$,} and temperature projections of the box at certain points in time.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/jlw_xe_bg_mass_weight.pdf}
    \caption{For the entire box, the mass-weighted average LW intensity from stars within the simulation is shown in solid red, and the fraction of the volume ionized above 10 per cent versus time is shown in solid black. The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}). \textbf{The solid red line in the legend refers to both the solid and dashed lines in the figure.} Temperature projections are shown at the points indicated by the arrows.}
    \label{fig:JLW_xe_mass}
\end{figure}

In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39. The corresponding \textbf{comoving} star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases. The SFRD sharply declines near the end of the simulation but does not drop to zero. Small volumes are subject to cosmic variance, in particular the formation time of the first galaxies, which generates the bulk of the LW radiation background.  This SFRD is therefore not representative of a cosmological average.  In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}. \textbf{\citet{Xu13} and \citet{Magg16} see a SFRD of $~10^{-4}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 15$ and $z = 20$ respectively. \citet{Jaacks19} find a SFRD of $~10^{4.5}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 20$, which flattens out to $10^{-3}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ by $z =7$.} \textbf{Our} SFRD rates are consistent with \textbf{these} other studies, but it is likely to change depending on the particular modes captured by the initial conditions.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
    \caption{The \textbf{comoving} star formation rate density of Pop III stars. The SFRD peaks at a redshift of 20, and slowly falls off. Note that metal-enriched star formation continually increases throughout time, although that is not plotted here. Due to the small box size of our simulation, this SFRD is particular for our box.}
    \label{fig:pop3_SFR_bar}
\end{figure}

@@

The LW background intensity \textbf{at the instance of Pop III star formation} versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}. Because the LW background only varies by a factor of five as Pop III stars form, most points lie within a small intensity range, just below $1~J_{21}$. Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq. \ref{mthresh}) for the given LW background (Eq. \ref{LWbg}) is the solid black line. We see again that almost all haloes form Pop III stars below the M01 threshold. There are also a few haloes that form Pop III stars in very high $J_{\rm LW}$, below the relation. This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other. Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation. The high $J_{\rm LW}$ is generally an indicator that the haloes will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other. As there are only a few data points in this region, this situation is rare. It should be noted that there are duplicate haloes within this plot, since haloes are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation. The grouped points in the higher end of $J_{\rm LW}$ are representative of such haloes.

We find that a total of 84\% of the haloes forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range.  Given that the background intensity only varies by a factor of five, previous work suggested that most haloes should have formed stars around or above the M01 relationship.  However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the \textbf{instantaneous} LW intensity and the host halo mass. This behavior suggests that the LW intensity is not the primary indicator of the mass at which a metal-free halo collapses. \hh{} self-shielding is the main cause behind this conclusion because the internal dynamics and chemo-thermal evolution are now isolated from its large-scale environment and mostly depends on the local conditions within the halo. \textbf{Alternatively, it is possible that there could be a correlation between the time-integrated LW background and the host halo mass. These calculations are outside the scope of this paper and require further study.}

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. We are only tracking \textbf{star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.  Furthermore, we are not modeling the formation of low-mass stars ($<1~\Ms$) that may form out of fragmented gas at higher densities and smaller scales.  Thus our results in this section should be considered as lower limits to the number of Pop III stars.}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
    \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works. The black solid line is from M01 given our LW background, blue solid line from \citet{Trenti09_SFR} at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}. $J_{LW}$ = 0 for the various sources is plotted here at $J_{\rm LW}$/$J_{21}$ = 10$^{-4}$. \textbf{The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}} The solid bands of halo masses correspond to the characteristic masses of haloes to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}. For each band, the maximum halo mass occurs at $z = 15$. For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 \kms{} at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively. \textbf{The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}}
    \label{fig:compare_JLW_mass}
\end{figure}

@@

There are a few minor shortcomings to this work that should be noted. \textbf{As discussed in \S2.2.1, the number of Pop III star particles that form is insensitive to merging distances in our formation algorithm down to 0.625 pc. Since this value is larger than fragmentation scales within molecular cores, it is possible that our Pop III star particles are sites for multiple Pop III star formation. With this in mind, our multiplicity results are only strengthened by the possibility of having more Pop III stars forming at these locations.}

@@

\textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within haloes for varying streaming velocities, showed that high streaming velocities could restrict first star formation to atomic cooling haloes in the most extreme cases. Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines in Figure \ref{fig:compare_JLW_mass}. \citet{Hirano17_Science} investigated the effect that streaming velocities have on massive black hole seed formation and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihaloes up to the atomic cooling limit.}

\textbf{The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8\kms$ at $z=199$) would affect haloes below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.  Our results sample minihaloes that experience such streaming velocities primarily at $z < 20$, whereas \citet{Hirano17_Science} studied much earlier structure formation. In the evolution of a halo affected by streaming velocities, it would have started to accumulate gas once above these critical masses while also being irradiated by a LW background.  Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our main conclusion that \hh{} plays an important role in Pop III star formation.}

@@

\begin{itemize}
	\item We find that Pop III stars are forming in haloes with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item \hh{} self-shielding allows haloes below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.  Self-shielding creates a disconnect between the \textbf{instantaneous} LW background and the collapse, resulting in a broad mass distribution of metal-free star forming haloes and no strict correlation between the two quantities.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, haloes with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass haloes, resulting in galaxies with young and old metal-free stars. 
\end{itemize}

>>>>

In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background at the instance of star formation, augmenting results from prior work. We aim to provide further insight into the host haloes of Pop III stars. In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding are described. In \S 3 we present the results of our analysis. In \S 4 we discuss the results in more detail and compare with previous work. In \S 5 we conclude our discussion with a summary of our results and the implications therein.

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter particle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior. The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$. The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.

@@

If within 10 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance. We ran another 1~Mpc$^3$ simulation with the same setup as the main simulation with the exception that it was a zoom-in simulation focusing on a single minihalo of mass $5 \times 10^5~\Ms$ collapsing at $z \simeq 23$.  Starting from 1~Myr before the collapse, we followed Pop III star formation in this one halo with a merging distance of 10, 5, 2.5, 1.25, and 0.625~pc.  We found that even when this number was decreased to 0.625 pc, the number of star particles that formed was unchanged.  We note that our density threshold for star particle formation is equivalent to a molecular core.  Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU within molecular cores \citep[e.g.][]{Turk09, Stacy11}, therefore our results on multiplicity should be considered as lower limits.

The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from the W12 choice of 100 M$_{\odot}$. This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above. The Pop III IMF mass ranges from $1 \leq M / M_{\odot} \leq 300$. Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. Again, we are only tracking the formation of metal-free molecular cores, which form either a single or multiple massive Pop III stars and perhaps several more low mass stars.

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a realistic \hh{} halo profile, and use Equation \ref{shield} to calculate the shielding factor. The \hh{} molecule number density within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density. Here, H$_{0}$ is the Hubble constant, G is the gravitational constant, and z is the redshift. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift, and for a given \hh{} fraction halo profile. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at $z = 24.1$ from \citet{OShea08} (their Figure 13d) with $J_{21} = 0$, which was extracted directly from their plot. These profiles were approximated with a piecewise power-law for simplicity given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(r) - 3.039$ for $r < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(r) - 2.737$ for $r > 3.5$ pc. 
As the halo masses increase, the shielding factor decreases, meaning there is more shielding occurring within that halo. This behavior occurs because as halo masses increase, more \hh{} is being added to the calculation of the column density. The more \hh{} present within a halo, the smaller the shielding factor will become. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a Doppler broadening parameter $ b = 10 \kms$. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these haloes is almost at a maximum. Self-shielding will then significantly decrease the dissociation rate of \hh{} in the halo core, allowing for the presence of a significant \hh{} fraction even in a strong LW background.

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ haloes that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. When the first Pop III star forms in our simulation at $z = 27$, there are only 6 haloes that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}. These Pop III stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, haloes form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity coming from stars within the simulation as a function of time, the LW background given by Equation \ref{LWbg} in units of $J_{21}$, and temperature projections of the box at certain points in time.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/jlw_xe_bg_mass_weight.pdf}
    \caption{For the entire box, the mass-weighted average LW intensity from stars within the simulation is shown in solid red, and the fraction of the volume ionized above 10 per cent versus time is shown in solid black. The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}). The solid red line in the legend refers to both the solid and dashed lines in the figure. Temperature projections are shown at the points indicated by the arrows.}
    \label{fig:JLW_xe_mass}
\end{figure}

In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39. The corresponding comoving star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases. The SFRD sharply declines near the end of the simulation but does not drop to zero. Small volumes are subject to cosmic variance, in particular the formation time of the first galaxies, which generates the bulk of the LW radiation background.  This SFRD is therefore not representative of a cosmological average.  In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}. \citet{Xu13} and \citet{Magg16} see a SFRD of $~10^{-4}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 15$ and $z = 20$ respectively. \citet{Jaacks19} find a SFRD of $~10^{4.5}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 20$, which flattens out to $10^{-3}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ by $z =7$. Our SFRD rates are consistent with these other studies, but it is likely to change depending on the particular modes captured by the initial conditions.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
    \caption{The comoving star formation rate density of Pop III stars. The SFRD peaks at a redshift of 20, and slowly falls off. Note that metal-enriched star formation continually increases throughout time, although that is not plotted here. Due to the small box size of our simulation, this SFRD is particular for our box.}
    \label{fig:pop3_SFR_bar}
\end{figure}

@@

The LW background intensity at the instance of Pop III star formation versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}. Because the LW background only varies by a factor of five as Pop III stars form, most points lie within a small intensity range, just below $1~J_{21}$. Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq. \ref{mthresh}) for the given LW background (Eq. \ref{LWbg}) is the solid black line. We see again that almost all haloes form Pop III stars below the M01 threshold. There are also a few haloes that form Pop III stars in very high $J_{\rm LW}$, below the relation. This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other. Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation. The high $J_{\rm LW}$ is generally an indicator that the haloes will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other. As there are only a few data points in this region, this situation is rare. It should be noted that there are duplicate haloes within this plot, since haloes are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation. The grouped points in the higher end of $J_{\rm LW}$ are representative of such haloes.

We find that a total of 84\% of the haloes forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range.  Given that the background intensity only varies by a factor of five, previous work suggested that most haloes should have formed stars around or above the M01 relationship.  However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the instantaneous LW intensity and the host halo mass. This behavior suggests that the LW intensity is not the primary indicator of the mass at which a metal-free halo collapses. \hh{} self-shielding is the main cause behind this conclusion because the internal dynamics and chemo-thermal evolution are now isolated from its large-scale environment and mostly depends on the local conditions within the halo. Alternatively, it is possible that there could be a correlation between the time-integrated LW background and the host halo mass. These calculations are outside the scope of this paper and require further study.

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. We are only tracking star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.  Furthermore, we are not modeling the formation of low-mass stars ($<1~\Ms$) that may form out of fragmented gas at higher densities and smaller scales.  Thus our results in this section should be considered as lower limits to the number of Pop III stars.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
    \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works. The black solid line is from M01 given our LW background, blue solid line from \citet{Trenti09_SFR} at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}. $J_{LW}$ = 0 for the various sources is plotted here at $J_{\rm LW}$/$J_{21}$ = 10$^{-4}$. The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}. The solid bands of halo masses correspond to the characteristic masses of haloes to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}. For each band, the maximum halo mass occurs at $z = 15$. For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 \kms{} at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively. The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}
    \label{fig:compare_JLW_mass}
\end{figure}

@@

There are a few minor shortcomings to this work that should be noted. As discussed in \S2.2.1, the number of Pop III star particles that form is insensitive to merging distances in our formation algorithm down to 0.625 pc. Since this value is larger than fragmentation scales within molecular cores, it is possible that our Pop III star particles are sites for multiple Pop III star formation. With this in mind, our multiplicity results are only strengthened by the possibility of having more Pop III stars forming at these locations.

@@

A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within haloes for varying streaming velocities, showed that high streaming velocities could restrict first star formation to atomic cooling haloes in the most extreme cases. Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines in Figure \ref{fig:compare_JLW_mass}. \citet{Hirano17_Science} investigated the effect that streaming velocities have on massive black hole seed formation and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihaloes up to the atomic cooling limit.

The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8\kms$ at $z=199$) would affect haloes below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.  Our results sample minihaloes that experience such streaming velocities primarily at $z < 20$, whereas \citet{Hirano17_Science} studied much earlier structure formation. In the evolution of a halo affected by streaming velocities, it would have started to accumulate gas once above these critical masses while also being irradiated by a LW background.  Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our main conclusion that \hh{} plays an important role in Pop III star formation.

@@

\begin{itemize}
	\item We find that Pop III stars are forming in haloes with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item \hh{} self-shielding allows haloes below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.  Self-shielding creates a disconnect between the instantaneous LW background and the collapse, resulting in a broad mass distribution of metal-free star forming haloes and no strict correlation between the two quantities.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, haloes with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass haloes, resulting in galaxies with young and old metal-free stars. 
\end{itemize}
